How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-23 tse-paper/content.tex
Paper edits

\begin{figure}[!t]
	\centering
	\includegraphics[page=2, width=\columnwidth, trim={0cm 1cm 1.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
	\caption{Study design of our technique comparison study.}
	\label{fig:study}
\end{figure}

@@

\subsection{Common Text Similarity (CTS)}

@@

\subsection{Keyword Search (KWS)}

@@

\subsection{Program Synthesis by Example (PBE)}

@@

\subsection{Comparison of All Techniques}
\Cref{fig:success-partial-all} compares the success of all chunk retrieval by the different techniques in our study.
CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.

>>>>

\begin{figure*}[!t]
	\centering
	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
	\caption{Study design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

@@

\newpage
\subsection{Common Text Similarity (CTS)}

@@

\newpage
\subsection{Keyword Search (KWS)}

@@

\newpage
\subsection{Program Synthesis by Example (PBE)}

@@

\subsection{Comparison of All Techniques}
\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
